Transforming Trash as an Artistic Act

### 2015-12-06 chapter2_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

%
%
\summary{Factors that cause over consumption habits}
Technological advancements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labor and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

@@

%
%
[Art] There are some artists whose works are related with the phenomena expressed above. (Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.

@@

Zizek's argument can bring minds to the question that is our home going to be turned to trash home? Actually an artist work is related with not wasting. \todo{details}

>>>>

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labor and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

@@

%
%
\summary{Art}
There are some artists whose works are related with the phenomena expressed above. (Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.

@@

Zizek's argument can bring minds to the question that is our home going to be turned to trash home? Actually an artist work is based on habit of not wasting. In the installation thousands of items are displayed. They are saved instead of throwing. \todo{details}
